{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Slide 1 GPM

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantQ95}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<3|only@3> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
        different current even though obtained at different values of $\Lambda_{div}$. 
      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
        $\Lambda_{div}$ without sensible difference among the current
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

>>>>

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=.8\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    %\centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantQ95}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> We repeat the same excercise at TCV with a
        slight difference in the profile of parallel connection
        length. This required operation at unusual low toroidal field
        (up to 0.8T)
      \item<4|only@4> At TCV,  no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> Observed and higher neutral pressure at the
        target whenever current is increased  
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}
